Deep Learning \\ NATURE Review Article

### 2015-09-23 Deep-Learning-Nature-Review.tex

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{times}
\usepackage{url}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

A nice example of the use of backpropagation is how it can be used to learn
representations for symbols, such as words. ~\citet{Hinton86b} introduced the idea
of learning a distributed representation for symbols and \citet{BenDucVin01-short}
showed how to combine the idea of learning a distributed
representation for each word with the task of modeling the probability
distribution of sequences of words (sentences from a corpus of text). We
have basically the composition two components: (1) mapping each of the
previous words in the sentence to their representation, and (2) mapping the
concatenation of these representations to a prediction for the
representation of the next word, from which one can compute its
probability.  Like in other applications of back-propagation, there seems
to be a chicken-and-egg problem, in the sense that the mapping (2) relies
on the word representations in (1), while it is the objective of achieving
the task performed by (2) that pushes the word representations in (1) to be
meaningful. It works because both are learned together, by a large number
of small gradual changes. The result is that words that are semantically
similar in the sense of being exchangeable end up nearly with the same
representation: one can replace ``funny'' by ``comical'' in many sentences and
the sentence remains plausible, so these two words have almost the same
representation. Similarly, ``Tuesday'' and ``Wednesday'' are exchangeable in
most sentences, so they end up very close to each other, while ``dog'' and
``cat'' are not always exchangeable but often are, so they are not too far
from each in that space. Furthermore, the way in which the representations
for related words differ ends up being also meaningful: the difference
between the representation for ``king'' and the representation for ``queen'' is
very close the difference between the representation for ``man'' and the
representation for ``woman'' \citep{Mikolov-et-al-ICLR2013}. The system has discovered
features, such as gender in the above example, and learned to map each word
to its proper features.

\begin{figure}[H]
\centerline{\includegraphics[width=0.7\linewidth]{fig-hidden-recurrence-rnn.png}}
\caption{(a better figure can be made)}
\end{figure}

@@

A particularly interesting and general form of neural network is the
recurrent neural network. It can process temporally structured data, by
scanning through it just like humans and animals do: at each time step the
neural network “sees” as input the next element of the sequence, and
changes its internal state , which is therefore a representation of all the
previously seen elements . We can think of the brain as an enormous
recurrent neural network: the activity of all the neurons at a given time
constitutes the state of the brain recurrent network. Your next visual
saccade may provide the next input to the brain’s recurrent network. A
recurrent network can also have outputs, corresponding to actions or
predictions, and the training objective for a recurrent networks is
obtained from these values. For example, a recurrent network for language
modeling has output units that predict the next word in the sequence. At
each time step it gets a new word as input and updates its state. Such a
network can also “imagine” a plausible sequence, which makes it a so-called
generative model.  At each time step, given the current state, the network
makes a probabilistic guess about the next word, say, given the previous
words. By randomly choosing the next word according to these probabilities,
one more element is added to the sequence, which becomes an input used to
update the state and predict the next word. Begin by thinking of the first
word to type, then type it. In general, given the words already typed,
think of the next word to type that would be compatible with those you
already wrote, etc. Maximizing the training criterion for such a recurrent
network also maximizes the probability that the recurrent network will
generate sequences such as those in the training corpus.

The challenge of training very deep nets and recurrent networks over long sequences

@@

\begin{verbatim}
We will explain the breakthrough that occurred in 2006 when an effective
 new way of learning multiple layers of features was discovered. The idea
 is to learn the layers one a time with the objective being to build a good
 model of the correlations between feature activities in the previous layer
 (or the input).  After this layer-by-layer unsupervised "pre-training" to
 discover features, backpropagation works very well for fine-tuning the
 features that have already been discovered.  Will we describe several
 variations of the pre-training methods.
\end{verbatim}

@@

Prior to 2006, most attempts at training multi-layered neural networks with
more than a few layers had failed and did not have any impact. However, a
few researchers, including the authors of this paper, continued searching
for ways to train deep neural networks, and many of them joined forces in a
Canadian research program with international nodes, called NCAP (Neural
Computation and Adaptive Perception), funded by the Canadian Institute For
Advanced Research (CIFAR), and headed by Geoff Hinton (and since 2014, by
Yoshua Bengio and Yann LeCun). In 2006, these researchers put out several
papers~\citep{Hinton06, Bengio-nips-2006-small,ranzato-07-small} outlining a general strategy for taking advantage of
unsupervised learning of individual layers of a deep neural network in
order to initialize (or pre-train) a deep supervised network. Unlike
supervised learning, unsupervised learning only needs to look at the input
of the neural network, not the targets that we want to associate with these
inputs, so it can take advantage of large quantities of unlabeled data (for
which no target is given, which have not been examined and tagged by
humans) and even data associated with other tasks (see ‘transfer learning’,
below).  These unsupervised learning algorithm produce a new representation
of the data by learning the synaptic weights of a new layer of neurons that
map the raw input (or the output of the previous layer) to a new set of
learned features. Whereas traditional machine learning is based on
hand-crafted features, deep learning aims at taking advantage of data
(potentially unlabeled) in order to discover good features. This raises a
very good and difficult question: what is a good representation? Different
deep learning algorithms answer this question in different ways, but the
general idea is that a good representation makes it easier to learn further
dependencies, either between the features themselves (e.g., they are
independent or just linearly related to each other), or between the
features and some target variables (if we want to predict some categories,
given these features). An important ingredient of these 2006 papers is
that, although the job of learning a good representation is difficult,
unsupervised learning allows to improve a representation by iteratively
transforming previous representations. In these experiments, a new
Restricted Boltzmann Machine or auto-encoder is trained for creating the
next layer, and the representation learned can be used as input to train
the next layer similarly. After adding several such layers, one can
consider the overall mapping from input to top-level representation as the
initialization for a deep supervised neural network, which is further
trained with respect to the supervised objective (e.g., minimizing
classification error). We call this stage supervised fine-tuning because
all the layers are adjusted with respect to a single global objective,
after having been initialized from layer-wise unsupervised pre-training.

>>>>

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{times}
\usepackage{url}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

\addtolength{\textwidth}{2cm}
%\addtolength{\textwidth}{1cm}
\addtolength{\textheight}{2cm}
%\addtolength{\textheight}{1cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}

@@

A nice example of the use of backpropagation is how it can be used to learn
representations for symbols, such as words. ~\citet{Hinton86b} introduced the idea
of learning a distributed representation for symbols and \citet{BenDucVin01-short}
showed how to combine the idea of learning a distributed
representation for each word with the task of modeling the probability
distribution of sequences of words (sentences from a corpus of text). We
have basically the composition of two components: (1) mapping each of the
previous words in the sentence to their representation, and (2) mapping the
concatenation of these representations to a prediction for the
representation of the next word, from which one can compute its
probability.  Like in other applications of back-propagation, there seems
to be a chicken-and-egg problem, in the sense that the mapping (2) relies
on the word representations in (1), while it is the objective of achieving
the task performed by (2) that pushes the word representations in (1) to be
meaningful. It works because both are learned together, by a large number
of small gradual changes. The result is that words that are semantically
similar in the sense of being exchangeable end up nearly with the same
representation: one can replace ``funny'' by ``comical'' in many sentences and
the sentence remains plausible, so these two words have almost the same
representation. Similarly, ``Tuesday'' and ``Wednesday'' are exchangeable in
most sentences, so they end up very close to each other, while ``dog'' and
``cat'' are not always exchangeable but often are, so they are not too far
from each in that space. Furthermore, the way in which the representations
for related words differ ends up being also meaningful: the difference
between the representation for ``king'' and the representation for ``queen'' is
very close to the difference between the representation for ``man'' and the
representation for ``woman'' \citep{Mikolov-et-al-ICLR2013}. The system has discovered
features, such as gender in the above example, and learned to map each word
to its proper features.

\iffalse
\begin{figure}[H]
\centerline{\includegraphics[width=0.7\linewidth]{fig-hidden-recurrence-rnn.png}}
\caption{(a better figure can be made)}
\end{figure}
\fi

@@

A particularly interesting and general form of neural network is the
recurrent neural network. It can process temporally structured data, by
scanning through it just like humans and animals do: at each time step the
neural network “sees” as input the next element of the sequence, and
changes its internal state , which is therefore a representation of all the
previously seen elements . We can think of the brain as an enormous
recurrent neural network: the activity of all the neurons at a given time
constitutes the state of the brain recurrent network. Your next visual
saccade may provide the next input to the brain’s recurrent network. A
recurrent network can also have outputs, corresponding to actions or
predictions, and the training objective for a recurrent network is
obtained from these values. For example, a recurrent network for language
modeling has output units that predict the next word in the sequence. At
each time step it gets a new word as input and updates its state. Such a
network can also “imagine” a plausible sequence, which makes it a so-called
generative model.  At each time step, given the current state, the network
makes a probabilistic guess about the next word, say, given the previous
words. By randomly choosing the next word according to these probabilities,
one more element is added to the sequence, which becomes an input used to
update the state and predict the next word. Begin by thinking of the first
word to type, then type it. In general, given the words already typed,
think of the next word to type that would be compatible with those you
already wrote, etc. Maximizing the training criterion for such a recurrent
network also maximizes the probability that the recurrent network will
generate sequences such as those in the training corpus.

\subsection{The challenge of training very deep nets and recurrent networks over long sequences}

@@

{\em
We will explain the breakthrough that occurred in 2006 when an effective
 new way of learning multiple layers of features was discovered. The idea
 is to learn the layers one at a time with the objective being to build a good
 model of the correlations between feature activities in the previous layer
 (or the input).  After this layer-by-layer unsupervised "pre-training" to
 discover features, backpropagation works very well for fine-tuning the
 features that have already been discovered.  Will we describe several
 variations of the pre-training methods.
}

@@

Prior to 2006, most attempts at training multi-layered neural networks with
more than a few layers had failed and did not have any impact. However, a
few researchers, including the authors of this paper, continued searching
for ways to train deep neural networks, and many of them joined forces in a
Canadian research program with international nodes, called NCAP (Neural
Computation and Adaptive Perception), funded by the Canadian Institute For
Advanced Research (CIFAR), and headed by Geoff Hinton (and since 2014, by
Yoshua Bengio and Yann LeCun). In 2006, these researchers put out several
papers~\citep{Hinton06, Bengio-nips-2006-small,ranzato-07-small} outlining a general strategy for taking advantage of
unsupervised learning of individual layers of a deep neural network in
order to initialize (or pre-train) a deep supervised network. Unlike
supervised learning, unsupervised learning only needs to look at the input
of the neural network, not the targets that we want to associate with these
inputs, so it can take advantage of large quantities of unlabeled data (for
which no target is given, which have not been examined and tagged by
humans) and even data associated with other tasks (see ‘transfer learning’,
below).  These unsupervised learning algorithms produce a new representation
of the data by learning the synaptic weights of a new layer of neurons that
map the raw input (or the output of the previous layer) to a new set of
learned features. Whereas traditional machine learning is based on
hand-crafted features, deep learning aims at taking advantage of data
(potentially unlabeled) in order to discover good features. This raises a
very good and difficult question: what is a good representation? Different
deep learning algorithms answer this question in different ways, but the
general idea is that a good representation makes it easier to learn further
dependencies, either between the features themselves (e.g., they are
independent or just linearly related to each other), or between the
features and some target variables (if we want to predict some categories,
given these features). An important ingredient of these 2006 papers is
that, although the job of learning a good representation is difficult,
unsupervised learning allows to improve a representation by iteratively
transforming previous representations. In these experiments, a new
Restricted Boltzmann Machine or auto-encoder is trained for creating the
next layer, and the representation learned can be used as input to train
the next layer similarly. After adding several such layers, one can
consider the overall mapping from input to top-level representation as the
initialization for a deep supervised neural network, which is further
trained with respect to the supervised objective (e.g., minimizing
classification error). We call this stage supervised fine-tuning because
all the layers are adjusted with respect to a single global objective,
after having been initialized from layer-wise unsupervised pre-training.
